Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-07-31 tex/scam/optimization.tex
boundedness

\begin{remark}
in sparsistency analysis, we assume that $L$, an upper bound to the coordinate-wise Lipschitz smoothness of the true function $f_0$, is known and that we constrain our estimate $\hat{f}$ to obey the same Lipschitz condition, that is, each $\hat{f}_k$ must be $L$-Lipschitz. This Lipschitz constraint can be easily added to our optimization program. In optimization~\ref{opt:alternate_opt}, we can enforce the Lipschitz condition by adding two constraints: $d_{k(1)} \geq - L$ and $\sum_{j=2}^{n-1} d_{k(j)} \leq L$ (similarly for optimization~\ref{opt:alternate_opt_concave}). We emphasize that we use the Lipschitz constraint only in our theoretical analysis; all of our experiments do not impose any Lipschitz condition.
\end{remark}

>>>>

\begin{remark}
in sparsistency analysis, we assume that $B$, an upper bound to $\| f^*_k \|_\infty$, is known and that we constrain our estimate $\hat{f}$ to obey the same boundedness condition, that is, for each $k$, we require that $\|\hat{f}_k\|_\infty \leq B$. This boundedness constraint can be easily added to our optimization program. In optimization~\ref{opt:alternate_opt}, we can enforce the boundedness condition by adding $p$ constraints: $\| \bar{\Delta}_k d_k \|_\infty \leq B$ for $k=1,...,p$. (similarly for optimization~\ref{opt:alternate_opt_concave}). We emphasize that we use the boundedness constraint only in our theoretical analysis; all of our experiments do not impose any boundedness condition.
\end{remark}

### 2014-07-31 tex/scam/sparsistency.tex
boundedness

Suppose $\lambda \leq c sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.

Suppose 
$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

@@

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} 
we have the following result.
\begin{corollary}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\

Suppose 
$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

>>>>

Suppose $\lambda \leq c_1 sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.  Suppose also that $\sigma \geq c_2$ for an arbitrarily small constant $c_2 > 0$.

Suppose 
$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$, where $c$ is a constant dependent only on $b, c_1, c_2$.\\

@@

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} 
we have the following result.
\begin{corollary}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. Suppose $\sigma \geq c_2$ for an arbitrarily small constant $c_2 > 0$.\\

Suppose 
$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$ where $c$ is some constant dependent only on $b, c_2$.\\
